---
title: "Israeli Palestinian Paper"
output: html_notebook
---
TEST
Loading data and setting up VAR model
```{r, echo=T}
library(tseries)
library(forecast)
library(astsa)
library(vars)
library(readxl)
library(expm)
library(imputeTS)
load("A:/College/Masters/2018 Spring/GSE 544/Project/Data.RData")
#data with mean removed
datam<-data.frame("attack"=ts(na.ma(x$att93miss, k = 24, weighting = "exponential")-mean(na.ma(x$att93miss, k = 24, weighting = "exponential")), start = 1987, frequency = 12),"repress"=ts(x$repress-mean(x$repress), start = 1987, frequency = 12),"concil"=ts(x$concil-mean(x$concil), start = 1987, frequency = 12))
#data without mean removed
data<-data.frame("attack"=ts(na.ma(x$att93miss, k = 24, weighting = "exponential"), start = c(1987,6), frequency = 12),"repress"=ts(x$repress, start = c(1987,6), frequency = 12),"concil"=ts(x$concil, start = 1987, frequency = 12))
var1<-VAR(data, lag.max=12, ic="AIC")
ts.plot(ts(data, start = c(1987,6), frequency=12), col=c("red","green","blue"), xlab="Year", ylab="# Events", main="Palestinian Attacks/Israeli Responses \n 1987-2004")
rect(xleft=1987,xright=1993,ybottom=-10, ytop=100,col = rgb(0,0,.2,.15), border = F)
rect(xleft=2000,xright=2004,ybottom=-10, ytop=100,col = rgb(0,0,.2,.15), border = F)
legend("topleft",legend = c("Attack","Repressive","Concilitory"),lty=c(1,1,1), col=c("red","green","blue"))
```
Checking Stability. Creating a 3x3 matrix because AIC saying one lag is best

```{r, echo=T}
A<-rbind(var1$varresult$attack$coefficients,var1$varresult$repress$coefficients,var1$varresult$concil$coefficients)
A<-A[,-10]
A<-rbind(A,cbind(diag(6),matrix(0,nrow = 6,ncol = 3)))
A
```

Checking Eigens:
```{r, echo=T}
e<-eigen(A)
abs(e$values)
```
Here, we see that our set is in fact stationary. Yay

Variance-Covariance matrix
```{r, echo=T}
v<-summary(var1)
vcov<-v$covres
vcorr<-v$corres
vcorr
vcov
```

Estimating A1
```{r, echo=T}
a1<-diag(3)-A[1:3,1:3]-A[1:3,4:6]-A[1:3,7:9]
a1
```

Finding $\theta_1$
```{r, echo=T}
Theta1=t(chol(solve(a1)%*%vcov%*%t(solve(a1))))
Theta1
B0inv=a1%*%Theta1
B0inv
BQ(var1)
```

#Creating Impulse Response Function for Attack, Repress, and Concil shock using Structural VAR
```{r, echo=T}
p<-12
J<-diag(ncol(data))
J<-cbind(J, matrix(rep(0,18), ncol = 6))

varirf<-irf(var1, cumulative = F, n.ahead = 100)
attackshock<-c(1,0,0)
repressshock<-c(0,1,0)
concilshock<-c(0,0,1)

attackresponse<-c(0,0,0)
concilresponse<-c(0,0,0)
repressresponse<-c(0,0,0)
for(i in 1:p){
  attackresponse=cbind(attackresponse,(((J%*%(A%^%i)%*%t(J)))%*%B0inv)%*%attackshock)
  repressresponse=cbind(repressresponse,(((J%*%(A%^%i)%*%t(J)))%*%B0inv)%*%repressshock)
  concilresponse=cbind(concilresponse,(((J%*%(A%^%i)%*%t(J)))%*%B0inv)%*%concilshock)
}
attackresponse<-attackresponse[,-1]
repressresponse<-repressresponse[,-1]
concilresponse<-concilresponse[,-1]

attackcumresp=matrix(nrow=3,ncol=p)
represscumresp=matrix(nrow=3,ncol=p)
concilcumresp=matrix(nrow=3,ncol=p)

for(i in 1:3){
  attackcumresp[i,]=cumsum(attackresponse[i,])
  represscumresp[i,]=cumsum(repressresponse[i,])
  concilcumresp[i,]=cumsum(concilresponse[i,])
}
par(mar = c(5,4,4,10))
plot(concilcumresp[1,], type="l", col="red", main="Impulse Response to Shock", xlab="Period After Shock",ylab="Cummulative Effect", lty=6, ylim=c(min(concilcumresp,attackcumresp,represscumresp),max(concilcumresp,attackcumresp,represscumresp)))
lines(concilcumresp[2,], col="green", lty=6)
lines(concilcumresp[3,], col="blue", lty=6)
lines(attackcumresp[1,], col="red", lty=1)
lines(attackcumresp[2,], col="green", lty=1)
lines(attackcumresp[3,], col="blue", lty=1)
lines(represscumresp[1,], col="red", lty=3)
lines(represscumresp[2,], col="green", lty=3)
lines(represscumresp[3,], col="blue", lty=3)
legend("right",legend = c("Attack Response","Repressive Response","Concilitory Response"), fill=c("red","green","blue"), xpd = T, inset=c(-.45,0), bty = "n")
legend("topright", legend = c("Attack Shock","Repress Shock", "Concilitory Shock"), lty = c(1,3,6), xpd = T, inset=c(-.41,.025), bty = "n", title="Legend")
```

#Creating Custom Shock Function for one Shock in Period 0
```{r, echo=T}
irfshock<-function(q, p){
  #a is attack shock
  #r is repressive shock
  #c is concilitory shock
  #p is number of periods ahead
  a<-q[1]
  r<-q[2]
  c<-q[3]
  if(length(q)!=3){
    return("error: q must be a vector of 3 elements. e.g. q<-c('attack shock', 'repressive shock', 'concilitory shock'")
  }
  else{
    if(p<=1){
      return("error: p must be >=1")
    }
    else{
      shock<-c(a,r,c) # c(attack, repress, concilitory)
      shockresponse<-c(0,0,0)
      for(i in 1:p){
        shockresponse=cbind(shockresponse,(((J%*%(A%^%i)%*%t(J)))%*%B0inv)%*%shock)
      }
      shockresponse<-shockresponse[,-1]

      shockcumresp=matrix(nrow=3,ncol=p)
    }
  
    colnames(shockcumresp)<-1:as.numeric(dim(shockcumresp)[2])
    row.names(shockcumresp)<-c("attack","repress","concilitory")
    colnames(shockresponse)<-1:as.numeric(dim(shockcumresp)[2])
    row.names(shockresponse)<-c("attack","repress","concilitory")

    ts.plot(shockresponse[1,], type = "l", col="red", main=paste("Impulse Response to Shock","c(",q[1],",",q[2],",",q[3],")", sep = " "), xlab="months after shock",ylab="effect (# of events)", ylim=c(min(shockresponse),max(shockresponse)))
    lines(shockresponse[2,], col="green")
    lines(shockresponse[3,], col="blue")

    if(max(shockresponse[,ncol(shockresponse)])<max(shockresponse[,1])){
      legend("topright",legend = c("Attacks","Repressive","Concilitory"), fill=c("red","green","blue"))
    }
    else{
      legend("bottomright",legend = c("Attacks","Repressive","Concilitory"), fill=c("red","green","blue"))
    }
    return(shockresponse)
    #return(shockresponse)
  }
}
```

#Multiple Shock. Here it's just 3
```{r}
a<-irfshock(c(1,0,0),12)+cbind(matrix(0, nrow = 3, ncol = 2),irfshock(c(0,1,0),12)[,-(11:12)])+cbind(matrix(0, nrow = 3, ncol = 3),irfshock(c(0,0,1),12)[,-(12:10)])
ts.plot(a[1,], col="red", ylim=c(min(a), max(a)), main="Impulse Response to Continuous Shocks", xlab="months after shock", ylab="effect (# of events)")
lines(a[2,], col="green")
lines(a[3,], col="blue")

```


```{r}
multipleshock=function(q,p){
  n=nrow(q)
  multishock=irfshock(q[1,],p)
  for(i in 2:n){
    s=irfshock(q[i,],p)
    shift=matrix(0,nrow=3,ncol=i-1)
    combined=cbind(shift,s)[,1:12]
    multishock=multishock+combined
  }
  return(multishock)
}
```

```{r}
test=matrix(diag(3),nrow=3,ncol=3)
a=multipleshock(test,12)
ts.plot(a[1,], col="red", ylim=c(min(a), max(a)), main="Impulse Response to Multiple Shocks", xlab="months after shock", ylab="effect (# of events)")
lines(a[2,], col="green")
lines(a[3,], col="blue")
```

